---
title: "TCSAM2013 Model Results: Figures"
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
output: word_document
fontsize: 11pt
params: 
    paths: none
    obj: none
    numRecent: 15
    plot1stObs: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE,
                      dpi=300,fig.width=6.5,fig.height=3.9)
```

```{r init}
    require(pander);
    require(ggplot2);
    require(ggthemes);
    require(reshape2);
    require(rTCSAM2013);
    require(wtsUtilities);
    panderOptions("table.caption.prefix","Table ")
    panderOptions("table.split.table",Inf)
    paths<-params$paths;
    obj<-params$obj;
    numRecent<-params$numRecent;
    plot1stObs<-as.logical(params$plot1stObs);
    figno<-1;
    tblno<-1;
    cat("Working dir = '",getwd(),"'\n\n");
```

#Input model cases
```{r getFiles}
    if (is.null(obj)){
        if (!is.character(paths)){
            cat("'paths' parameter is not a character vector!\n");
            stop();
        }
        obj<-list();
        for (case in names(paths)){
            cat(case,": '",paths[case],"'\n",sep='');
            res<-getResLst(inp.dir=paths[case]);
            if (is.null(res)) {
                #remove path from paths
                paths<-paths[names(paths)!=case];
            } else {
                #add res to obj list
                obj[[case]]<-res;
            }
            rm(res);
        }
    } else {
        obj<-convertToListOfResults(obj);
    }
    cases<-names(obj);
    ncases<-length(cases);
```

```{r printCases}
    if (!is.null(paths)){ 
        t<-as.data.frame(list(case=cases, path=getSubPaths(paths,last=3)));
        t$path<-paste0("'",t$path,"'");
    } else {
        t<-as.data.frame(list(case=cases));
    }
    row.names(t)<-NULL;
    pander(t,caption=paste0(tblno,". Model cases for comparison."));
    tblno<-tblno+1;
```

#Objective function components
```{r plots.OFCs1,results='asis'}
    plots<-compareModelResults.ObjFunComponents(obj,y='objFun',
                                                showPlot=FALSE);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Objective function component differences
```{r plots.OFCs2,results='asis'}
    if (length(cases)>1){
        plots<-compareModelResults.ObjFunComponents(obj,y="diff",
                                                    showPlot=FALSE);
        figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
        rm(plots);
    } else {
        cat("No differences plotted: only one model case considered.\n")
    }
```
  
#Parameter estimates
If available, parameter confidence intervals are +/- one standard deviation. Triangles indicate initial prameter values, circles represent final parameter values. Dark grey shading indicates parameter bounds (if any).
  
```{r doPlots.Parameters,results='asis'}
    plots<-compareModelResults.Params(obj,
                                      showPlot=FALSE);
```
  
```{r plots.Params.Population.Recruitment,results='asis'}
    ps<-plots[["population"]][["recruitment"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.Population.RecDevs,results='asis',fig.height=20,fig.width=12}
    ps<-plots[["population"]][["recruitment devs"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["population"]][["initial recruitment devs"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.Population.Other,results='asis'}
    ps<-plots[["population"]][["natural mortality multipliers"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["population"]][["growth"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.Population.PrM2M,results='asis',fig.height=20,fig.width=12}
    ps<-plots[["population"]][["molt-to-maturity: females"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["population"]][["molt-to-maturity: males"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.Surveys,results='asis',fig.height=10}
    ps<-plots$surveys[["surveys"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.SurveySelectivity,results='asis'}
    ps<-plots[["surveys"]][["survey selectivity"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.TCFMaleSelectivity,results='asis',fig.height=20,fig.width=12}
    ps<-plots[["fisheries"]][["TCF selectivity"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.TCFRetention,results='asis'}
    ps<-plots[["fisheries"]][["TCF retention"]];
    figno<-(printGGList(ps[[1]],figno=figno,cap=names(ps),show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.FisherySelectivity,results='asis',fig.height=20,fig.width=12}
    ps<-plots[["fisheries"]][["SCF selectivity"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["fisheries"]][["RKF selectivity"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["fisheries"]][["GTF selectivity"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.FisheryRates,results='asis',fig.height=10}
    ps<-plots[["fisheries"]][["mortality or capture rate"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps);
```
  
```{r plots.Params.FisheryDevs,results='asis',fig.height=20,fig.width=12}
    ps<-plots[["fisheries"]][["TCF mortality or capture rate devs"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["fisheries"]][["SCF mortality or capture rate devs"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["fisheries"]][["RKF mortality or capture rate devs"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    ps<-plots[["fisheries"]][["GTF mortality or capture rate devs"]];
    figno<-(printGGList(ps,figno=figno,show=TRUE))$figno;
    rm(ps,plots);
```
  
#Survey selectivity functions
```{r plots.SurveySelFcns,results='asis'}
    plots<-compareModelResults.SurveySelFcns(obj);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Fishery retention functions
Retained mortality or retention (GMacs FMM) functions for males in the directed fishery, pre-1991 and post-1990.
  
```{r plots.FisheryRetFcns,results='asis',fig.height=3}
    plots<-compareModelResults.FisheryRetFcns(obj);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Fishery selectivity functions
Bycatch selectivity functions for females in the directed fishery and males and females in the snow crab, BBRKC fisheries, and groundfish fisheries. Capture and/or total fishing mortality selectivity functions for males in the directed fishery prior to 1991.
  
```{r plots.FisherySelFcns,results='asis'}
    plots<-compareModelResults.FisherySelFcns(obj);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Fishery selectivity functions
Annual male total-catch capture and/or fishing mortality selectivity functions for the directed fishery 
starting in 1991/92. The directed fishery was closed during 1997/98-2004/05 and 2010/11-2012/13. During these time periods, the "mean" selectivity function that forms the 
basis for the annual deviations is shown.
  
```{r plots.FisheryTCFMaleSelFcns,results='asis',fig.height=9}
    plots<-compareModelResults.FisheryTCFMaleSelFcns(obj);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Population processes
```{r plots.PopProcesses,results='asis'}
    plots<-compareModelResults.PopProcesses(obj);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Population quantities
```{r plots.PopQuantities,results='asis'}
    plots<-compareModelResults.PopQuantities(obj,
                                            numRecent=numRecent);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Survey quantities
```{r plots.SurveyQuantities,results='asis'}
    plots<-compareModelResults.SurveyQuantities(obj,
                                                numRecent=numRecent,
                                                plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Survey size comps
```{r plots.SurveyZCs,results='asis',fig.height=20,fig.width=12}
    plots<-compareModelResults.SurveyZCs(obj,
                                         numRecent=numRecent,
                                         plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Pearson's residuals from survey size comps
```{r plots.SurveyPRs,results='asis',fig.height=8,fig.width=6.5}
    plots<-compareModelResults.SurveyPRs(obj,
                                         numRecent=numRecent,
                                         plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Survey mean size comps and effective sample sizes
```{r plots.SurveyMeanZCs,results='asis'}
    plots<-compareModelResults.SurveyMeanZCs(obj,
                                             numRecent=numRecent,
                                             plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Fisheries quantities
```{r plots.Fisheries,results='asis'}
    plots<-compareModelResults.FisheryQuantities(obj,
                                                numRecent=numRecent,
                                                plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```

#Fishery size comps
```{r plots.FisheryZCs,results='asis',,fig.height=20,fig.width=12}
    plots<-compareModelResults.FisheryZCs(obj,
                                          numRecent=numRecent,
                                          plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```

#Pearson's residuals from fishery size comps
```{r plots.FisheryPRs,results='asis',,fig.height=8,fig.width=6.5}
    plots<-compareModelResults.FisheryPRs(obj,
                                          numRecent=numRecent,
                                          plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```

#Fishery mean size comps and effective sample sizes
```{r plots.FisheryMeanZCs,results='asis'}
    plots<-compareModelResults.FisheryMeanZCs(obj,
                                             numRecent=numRecent,
                                             plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
#Fishery capture/mortality rates
```{r plots.FisheryRates,results='asis'}
    plots<-compareModelResults.FisheryRates(obj,
                                            numRecent=numRecent,
                                            plot1stObs=plot1stObs);
    figno<-(printGGList(plots,figno=figno,show=TRUE))$figno;
    rm(plots);
```
  
